Manuscript

### 2018-12-21 manuscript.tex
work on manuscript updates

G2P designed a set of standards for stratifying their database's cancer
variant interpretations, ranging from preclinical data at the
low-evidence end (level D) to clinically actionable interpretations at
the high-evidence end (level A). To test only these clinically
actionable associations, we filtered the G2P dataset for only level-A
G2P interpretations, of which there were 1,296 (see Methods). All
compounds screened within the GDSC, CTRP, and CCLE datasets are
considered \enquote{small molecules} and are respectively linked to
Compound (CID) numbers used for indexing in the PubChem database
(\url{https://pubchem.ncbi.nlm.nih.gov/}). As a result, non-small
molecules, which include proteins and biologics (i.e.~monoclonal
antibodies), that had level-A G2P evidence could not be included in our
comparisons. Thus, G2P interpretations for which the compound did not
have a matching CID code were excluded from further analysis as were
interpretations that did not have an associated compound, resulting in
removal of 402 interpretations (Table 1). It should be noted that
cisplatin, a small molecule, was excluded due to its being indexed with
a ChEMBLdb identifier (\url{https://www.ebi.ac.uk/chembl/}), which we
did not manually re-index to a CID to avoid accidental
mischaracterization.

After filtering, 894 level-A G2P interpretations were carried forward in
subsequent analyses, constituting 57 unique drugs and 34 unique genes in
88 distinct level-A combinations (Figure 1A). The number of level-A
interpretations per drug ranged from 1 to 176 (M = 15.7, SD = 34.6),
from 1 to 264 (M = 26.2, SD = 61.6) per gene, and for each level-A
drug-gene combination, the range was 1 to 103 (M = 10.1, SD = 19.8).
These unique drugs, genes, and combinations are hereafter referred to as
G2P drugs, G2P genes, and G2P associations. Of the 57 unique G2P drugs,
37 of them were screened in at least one of the drug screen datasets, 14
were screened in two of the three datasets, and only three drugs were
screened in all three datasets. The remaining 20 un-screened G2P drugs
suggests an incompleteness of these drug screens, though these projects
frequently release new screening data that may include these drugs in
future releases.

Using cell-line-specific point mutation annotations from the CCLE, we
compared z-score-transformed area under the dose-response curve (AUC)
distributions between mutant and wildtype cell lines for all G2P genes
for each G2P drug tested in the CCLE, CTRP, and GDSC drug screens
(Figures 1B and 2A). At uncorrected \(\alpha\) = 0.05, Wilcoxon rank-sum
tests revealed that in CCLE, the AUC distributions of mutant and
wildtype groups for 10 out of 170 (5.88\%) tested drug-gene combinations
were significantly different, 91 out of 918 (9.91\%) were significantly
different for CTRP, and 61 out of 850 (7.18\%) for GDSC. We observe
little concordance between the number of interpretations for each G2P
association and the significance of mutation status on AUC for said G2P
association, suggesting that mutation status alone is not a robust
predictor of clinically actionable genetic targets. This led us to
examine the correlations between AUC and gene expression and AUC and
copy number, two other genomic features that are known to associate with
cancer and drug response.

@@

We compared the distribution of level-A G2P associations (Figure 1A) and
the associated p-values from the mutation status comparisons (Figure 1B)
with a null distribution of p-values derived from all pairwise
combinations of G2P genes and the G2P drugs tested in each dataset, less
any of the 88 distinct combinations with G2P interpretations, i.e.~the
non-gray squares in the right heatmap of Figure 1A (Figure 3A). To
formally test concordance between clinically actionable variants and
drug screen results, we conducted an independent, two-group t-test to
compare the distributions of p-values of drug-gene combinations that
either were or were not represented with level-A evidence in G2P, which
indicated that the distributions of p-values did not significantly
differ for CCLE {[}t(9) = 0.25, p = 0.81{]}, CTRP {[}t(51) = 0.85, p =
0.40{]}, nor GDSC {[}t(47) = -0.56, p = 0.58{]} (Table 2). This further
supports that mutation status is not a robust genomic feature for
predicting therapeutic responses.

Similar tests were conducted for the distributions of Pearson
correlation coefficients (r) between the number of level-A G2P
associations and gene expression (RPKM) and copy number (log2 ratio) of
the gene in the association (Figures 3B-C). Example r derivations are
shown in Figures 2B-C. Absolute values of r were used to simplify
extreme values in both directions for testing. The difference in the
CCLE \textbar{}r\textbar{} distributions for both gene expression
{[}t(8) = 1.43, p = 0.19{]} and copy number {[}t(8) = 2.48, p = 0.23{]}
were non-significant, which is likely explained by the small sample size
since only five G2P drugs were screened in the CCLE dataset. For both
the CTRP and GDSC screens, \textbar{}r\textbar{} values for gene
expression correlations were significantly greater for the level-A G2P
associations than the null distribution {[}tCTRP(49) = 3.79, pCTRP
\textless{} 0.001; tGDSC(44) = 2.97, pGDSC = 0.005{]}. The
\textbar{}r\textbar{} distributions using copy number were also
significantly different for CTRP {[}t(49) = 2.48, p = 0.017{]} but not
for GDSC {[}t(44) = 1.95, p = 0.058{]}.

In all three datasets for both level-A G2P associations and null
distribution associations, there are more significant
\textbar{}r\textbar{} values when using gene expression as the genomic
feature than when using copy number (Table 2), which corresponds with
previous work showing that gene expression is an informative molecular
feature when assessing drug sensitivity (Jang et al., 2014; Sirota et
al., 2011). Additionally, in all cases, there are more significant r
values when using copy number than there are significant p-values from
the mutation status comparisons. Though observational, these results
suggest an order of predictive robustness for these three genomic
features when used in isolation: Gene expression \textgreater{} copy
number \textgreater{} mutation status. Additionally, across all three
genomic features, CTRP consistently identified a higher percentage of
its possible level-A G2P associations than GDSC, and similarly, GDSC
identified a higher percentage than CCLE. In the CCLE-GDSC debate,
inconsistency between the datasets was attributed to the groups using
two very different assays for generating AUC measurements though it was
undecided which was more accurate (Haibe-Kains et al., 2013; Jang et
al., 2014; Weinstein \& Lorenzi, 2013). Our results provide very
preliminary evidence that GDSC is more accurate than CCLE in regards to
reproducing clinical associations. However, CTRP may be even more
accurate than both GDSC and CCLE.

@@

At an alpha of 0.05, no DGLs were identified in the CCLE screen when
using mutation status as a correlate (n = 7), but CTRP and GDSC
identified six and five, respectively, in skin cancer, lung cancer, and
cancer. These significant associations did not hold after Bonferroni
correction in CTRP (n = 48, \(\alpha\)adjusted = 0.001) or GDSC (n = 39,
\(\alpha\)adjusted = 0.001).

When using gene expression as the genomic feature, three CCLE DGLs had
significant correlations at an adjusted alpha of 0.006 (n = 9). Two of
these three DGLs were also significantly correlated with copy number (n
= 9, \(\alpha\)adjusted = 0.006).

In CTRP, AUC of 19 DGLs significantly correlated with gene expression,
12 of which were significant after correction (n = 61,
\(\alpha\)adjusted = 0.0008). Copy number correlations were significant
for 12 DGLs, with three DGLs significant post-correction (n = 61,
\(\alpha\)adjusted = 0.0008).

AUC of 16 DGLs in GDSC significantly correlated with gene expression. At
an adjusted alpha of 0.0009 (n = 53) eight of them were significant.
Fewer DGLs were significant when correlating AUC with copy number with 6
significant at an alpha of 0.05 and 1 significant at an adjusted alpha
of 0.0009 (n = 53).

Interestingly, when we test the effect of mutation status on drug
response for the DGLs derived from all pairwise combinations of G2P
drugs and genes\ldots{} (Figure \#\#1).

@@

When we don't account for lineage, Wilcoxon rank-sum tests revealed that
mutations in eight of the 33 (24.2\%) G2P genes significantly correlated
with CERES score (\(\alpha\) = 0.05): KRAS (p \textless{} 0.001), BRAF
(p \textless{} 0.001), BRCA2 (p \textless{} 0.001), CYP19A1 (p = 0.004),
TSC2 (p = 0.005), JAK2 (p = 0.031), DPYD (p = 0.042), and UGT1A1 (p =
0.048). Gene expression (RPKM) of 17 (51.5\%) G2P genes significantly
correlated with CERES score, as did copy number (log2-ratio) for 14
(42.4\%) G2P genes (Figure \#\#2). For the purpose of comparison to the
drug screen data, if we treat CRISPR knockdown like a small-molecule
drug, then these results are similar to the results from CCLE, CTRP, and
GDSC (Table 2).

@@

In a lineage-agnostic context of the CRISPR screen, ERBB2 gene
essentiality score had a significant negative correlation with ERBB2
gene expression (p \textless{} 10-12, r = -0.31) and ERBB2 copy number
(p \textless{} 10-15, r = -0.34) (Figure \#\#2). Similarly, MET gene
essentiality also correlated with both MET gene expression (p
\textless{} 10-12, r = -0.31) and copy number (p \textless{} 10-8, r =
-0.25). Notably, BRCA1 also significantly correlated with both gene
expression (p \textless{} 0.001, r = 0.16) and copy number (p
\textless{} 0.01, r = 0.14). BRCA2 significantly correlated with all
three of the genomic features tested: gene expression (p \textless{}
0.05, r = 0.10), copy number (p \textless{} 10-7, r = 0.23), and
mutation status (p \textless{} 0.001).

@@

@@

Level-A G2P interpretations correspond to clinical evidence that
suggests efficacy of gene targets and/or drugs, and this work questions
whether these relationships manifest themselves in in vitro drug
screens. We have demonstrated that on its own, mutation status is not a
robust predictor of drug efficacy and that copy number and gene
expression fare better as predictors. However, for these three genomic
features in all three datasets, only 11.1\% (mutation status, 1 of 9,
CCLE) to 47.9\% (gene expression, 23 of 48, CTRP) (Table 2), of the
level-A G2P drug-gene associations in the respective dataset were
significant at an uncorrected \(\alpha\) = 0.05. This suggests that
while the drug screens successfully identify some clinically relevant
drug-gene associations, many associations are also missed, which raises
the question of the extent to which clinical researchers can rely on in
vitro drug screens when attempting to develop and select therapeutics
for cancer patients.

@@

The CCLE provided mutation annotations in 19,280 genes across 1,596 cell
lines (dataset: depmap\_18Q4\_mutation\_calls.csv, accessed 14 November
2018). CCLE called substitutions using MuTect (Cibulskis et al., 2013)
and annotated variants using Oncotator (Ramos et al., 2015) and indels
using Indelocator
(\url{https://software.broadinstitute.org/cancer/cga/indelocator}). We
filtered mutation calls for point mutations, defined as
single-nucleotide insertions, deletions, and substitutions, regardless
of result, i.e.~frameshift or missense mutation. For this analysis, cell
lines harboring non-silent point mutations were considered
\enquote{mutant} for the gene in question. All other mutations and genes
without annotation in the Mutation Annotation Format (MAF) file were
considered \enquote{wildtype.} \enquote{Mutant} and \enquote{wildtype}
calls were binarily encoded per-gene/per-cell line, regardless of
quantity of harbored mutations per gene in a given cell line.

@@

The CCLE reports cell line sensitivity to small molecules as an activity
area measured above the dose-response curve (ActArea), while both CTRP
and GDSC report small molecule activity as area under the dose-response
curve (AUC). Since ActArea is reported with a scale of 0 to 8, we
converted CCLE's ActArea values to AUC via:

@@

For Figure 1, all data were imported and manipulated using pandas
(v0.23.0) (McKinney, 2011) and plotted using seaborn (v0.90) (Waskom,
2012), which sat on top of matplotlib (v2.2.2) (Hunter, 2007) and was
executed on Python (v2.7.15) (Python Software Foundation,
\url{https://www.python.org/}) in an IPython (v5.5.0) (Pérez \& Granger,
2007) kernel within a localhost Jupyter (v5.2.2) notebook (Kluyver et
al., 2016). All other analyses were conducted in R (v3.5.0) (R
Foundation for Statistical Computing, \url{https://www.R-project.org/})
in an RStudio environment (v1.1.447) (RStudio, 2012). All other plots
were drawn using the ggplot2 (v3.0.0) R package (Wickham, 2016).

@@

@@

>>>>

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:table-g2p-nonCID}Distribution of level-A G2P drugs excluded from analyses}
\begin{tabular}{llll}
\toprule
Compound & \multicolumn{1}{c}{Compound identifier} & \multicolumn{1}{c}{Number of G2P interpretations} & \multicolumn{1}{c}{Proportion of excluded interpretations (\%)}\\
\midrule
cetuximab & CHEMBL1201577 & 74 & 18.41\\
cisplatin & CHEMBL2068237 & 3 & 0.75\\
egfr & SID160769799 & 1 & 0.25\\
ipilimumab & CHEMBL1789844 & 2 & 0.50\\
mab & CHEMBL2109423 & 16 & 3.98\\
nivolumab & CHEMBL2108738 & 4 & 1.00\\
panitumumab & CHEMBL1201827 & 75 & 18.66\\
pembrolizumab & CHEMBL3137343 & 3 & 0.75\\
pertuzumab & CHEMBL2007641 & 1 & 0.25\\
trastuzumab & CHEMBL1201585 & 9 & 2.24\\
NA & NA & 214 & 53.23\\
\bottomrule
\addlinespace
\end{tabular}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} mAb = monoclonal antibody; NA indicates G2P interpretation does not have an associated compound}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

G2P designed a set of standards for stratifying their database's cancer
variant interpretations, ranging from preclinical data at the
low-evidence end (level D) to clinically actionable interpretations at
the high-evidence end (level A). To test only these clinically
actionable associations, we filtered the G2P dataset for only level-A
G2P interpretations, of which there were 1,296 (see Methods). All
compounds screened within the GDSC, CTRP, and CCLE datasets are
considered \enquote{small molecules} and are respectively linked to
Compound (CID) numbers used for indexing in the PubChem database
(\url{https://pubchem.ncbi.nlm.nih.gov/}). As a result, non-small
molecules, which include proteins and biologics (i.e.~monoclonal
antibodies), that had level-A G2P evidence could not be included in our
comparisons. Thus, G2P interpretations for which the compound did not
have a matching CID code were excluded from further analysis as were
interpretations that did not have an associated compound, resulting in
removal of 402 interpretations Table~\ref{tab:table-g2p-nonCID}. It
should be noted that cisplatin, a small molecule, was excluded due to
its being indexed with a ChEMBLdb identifier
(\url{https://www.ebi.ac.uk/chembl/}), which we did not manually
re-index to a CID to avoid accidental mischaracterization.

After filtering, 894 level-A G2P interpretations were carried forward in
subsequent analyses, constituting 57 unique drugs and 34 unique genes in
88 distinct level-A combinations (\emph{Figure 1A}). The number of
level-A interpretations per drug ranged from 1 to 176 (\(M =\) 15.68,
\(SD =\) 34.63), 1 to 264 (\(M =\) 26.24, \(SD =\) 61.58) per gene, and
for each level-A drug-gene combination, the range was 1 to 103 (\(M =\)
10.14, \(SD =\) 19.80). These unique drugs, genes, and combinations are
hereafter referred to as G2P drugs, G2P genes, and G2P associations. Of
the 57 unique G2P drugs, 37 of them were screened in at least one of the
drug screen datasets, 14 were screened in two of the three datasets, and
only three drugs were screened in all three datasets. The remaining 20
un-screened G2P drugs suggests an incompleteness of these drug screens,
though these projects frequently release new screening data that may
include these drugs in future releases.

Using cell-line-specific point mutation annotations from the CCLE, we
compared z-score-transformed area under the dose-response curve (AUC)
distributions between mutant and wildtype cell lines for all G2P genes
for each G2P drug tested in the CCLE, CTRP, and GDSC drug screens
(\emph{Figures 1B and 2A}). At uncorrected \(\alpha = 0.05\), Wilcoxon
rank-sum tests revealed that in CCLE, the AUC distributions of mutant
and wildtype groups for 10 out of 170 (5.88\%) tested drug-gene
combinations were significantly different, 91 out of 918 (9.91\%) were
significantly different for CTRP, and 61 out of 850 (7.18\%) for GDSC.
We observe little concordance between the number of interpretations for
each G2P association and the significance of mutation status on AUC for
said G2P association, suggesting that mutation status alone is not a
robust predictor of clinically actionable genetic targets. This led us
to examine the correlations between AUC and gene expression and AUC and
copy number, two other genomic features that are known to associate with
cancer and drug response.

@@

We compared the distribution of level-A G2P associations (\emph{Figure
1A}) and the associated p-values from the mutation status comparisons
(\emph{Figure 1B}) with a null distribution of p-values derived from all
pairwise combinations of G2P genes and the G2P drugs tested in each
dataset, less any of the 88 distinct combinations with G2P
interpretations, i.e.~the non-gray squares in the right heatmap of
\emph{Figure 1A (Figure 3A}). To formally test concordance between
clinically actionable variants and drug screen results, we conducted an
independent, two-group t-test to compare the distributions of p-values
of drug-gene combinations that either were or were not represented with
level-A evidence in G2P, which indicated that the distributions of
p-values did not significantly differ for CCLE {[}t(9) = 0.25, p =
0.81{]}, CTRP {[}t(51) = 0.85, p = 0.40{]}, nor GDSC {[}t(47) = -0.56, p
= 0.58{]} (Table 2). This further supports that mutation status is not a
robust genomic feature for predicting therapeutic responses.

Similar tests were conducted for the distributions of Pearson
correlation coefficients (r) between the number of level-A G2P
associations and gene expression (RPKM) and copy number (log2 ratio) of
the gene in the association (\emph{Figures 3B-C}). Example r derivations
are shown in \emph{Figures 2B-C}. Absolute values of r were used to
simplify extreme values in both directions for testing. The difference
in the CCLE \textbar{}r\textbar{} distributions for both gene expression
{[}t(8) = 1.43, p = 0.19{]} and copy number {[}t(8) = 2.48, p = 0.23{]}
were non-significant, which is likely explained by the small sample size
since only five G2P drugs were screened in the CCLE dataset. For both
the CTRP and GDSC screens, \textbar{}r\textbar{} values for gene
expression correlations were significantly greater for the level-A G2P
associations than the null distribution {[}tCTRP(49) = 3.79, pCTRP
\textless{} 0.001; tGDSC(44) = 2.97, pGDSC = 0.005{]}. The
\textbar{}r\textbar{} distributions using copy number were also
significantly different for CTRP {[}t(49) = 2.48, p = 0.017{]} but not
for GDSC {[}t(44) = 1.95, p = 0.058{]}.

In all three datasets for both level-A G2P associations and null
distribution associations, there are more significant
\textbar{}r\textbar{} values when using gene expression as the genomic
feature than when using copy number (Table 2), which corresponds with
previous work showing that gene expression is an informative molecular
feature when assessing drug sensitivity (Jang et al., 2014; Sirota et
al., 2011). Additionally, in all cases, there are more significant r
values when using copy number than there are significant p-values from
the mutation status comparisons. Though observational, these results
suggest an order of predictive robustness for these three genomic
features when used in isolation: Gene expression \textgreater{} copy
number \textgreater{} mutation status. Additionally, across all three
genomic features, CTRP consistently identified a higher percentage of
its possible level-A G2P associations than GDSC, and similarly, GDSC
identified a higher percentage than CCLE. In the CCLE-GDSC debate,
inconsistency between the datasets was attributed to the groups using
two very different assays for generating AUC measurements though it was
undecided which was more accurate(Haibe-Kains et al., 2013; Jang et al.,
2014; Weinstein \& Lorenzi, 2013). Our results provide very preliminary
evidence that GDSC is more accurate than CCLE in regards to reproducing
clinical associations. However, CTRP may be even more accurate than both
GDSC and CCLE.

@@

At an \(\alpha = 0.05\), no DGLs were identified in the CCLE screen when
using mutation status as a correlate (n = 7), but CTRP and GDSC
identified six and five, respectively, in skin cancer, lung cancer, and
cancer. These significant associations did not hold after Bonferroni
correction in CTRP (\(n = 48\), \(\alpha_{adjusted} = 0.001\)) or GDSC
(\(n = 39\), \(\alpha_{adjusted} = 0.001\)).

When using gene expression as the genomic feature, three CCLE DGLs had
significant correlations at an adjusted \(\alpha = 0.006\) (\(n = 9\)).
Two of these three DGLs were also significantly correlated with copy
number (\(n = 9\), \(\alpha_{adjusted} = 0.006\)).

In CTRP, AUC of 19 DGLs significantly correlated with gene expression,
12 of which were significant after correction (\(n = 61\),
\(\alpha_{adjusted} = 0.0008\)). Copy number correlations were
significant for 12 DGLs, with three DGLs significant post-correction
(\(n = 61\), \(\alpha_{adjusted} = 0.0008\)).

AUC of 16 DGLs in GDSC significantly correlated with gene expression. At
an adjusted \(\alpha\) of 0.0009 (\(n = 53\)) eight of them were
significant. Fewer DGLs were significant when correlating AUC with copy
number with 6 significant at an \(\alpha\) of 0.05 and 1 significant at
an adjusted \(\alpha\) of 0.0009 (\(n = 53\)).

Interestingly, when we test the effect of mutation status on drug
response for the DGLs derived from all pairwise combinations of G2P
drugs and genes\ldots{} (\emph{Figure \#\#1}).

@@

When we don't account for lineage, Wilcoxon rank-sum tests revealed that
mutations in eight of the 33 (24.2\%) G2P genes significantly correlated
with CERES score (\(\alpha = 0.05\)): KRAS (\(p < 0.001\)), BRAF
(\(p < 0.001\)), BRCA2 (\(p < 0.001\)), CYP19A1 (\(p = 0.004\)), TSC2
(\(p = 0.005\)), JAK2 (\(p = 0.031\)), DPYD (\(p = 0.042\)), and UGT1A1
(\(p = 0.048\)). Gene expression (RPKM) of 17 (51.5\%) G2P genes
significantly correlated with CERES score, as did copy number
(log2-ratio) for 14 (42.4\%) G2P genes (Figure \#\#2). For the purpose
of comparison to the drug screen data, if we treat CRISPR knockdown like
a small-molecule drug, then these results are similar to the results
from CCLE, CTRP, and GDSC (Table 2).

@@

In a lineage-agnostic context of the CRISPR screen, ERBB2 gene
essentiality score had a significant negative correlation with ERBB2
gene expression (\(p < 10^{-12}\), \(r = -0.31\)) and ERBB2 copy number
(\(p < 10^{-15}\), \(r = -0.34\)) (\emph{Figure \#\#2}). Similarly, MET
gene essentiality also correlated with both MET gene expression
(\(p < 10^{-12}\), \(r = -0.31\)) and copy number (\(p < 10^{-8}\),
\(r = -0.25\)). Notably, BRCA1 also significantly correlated with both
gene expression (\(p < 0.001\), \(r = 0.16\)) and copy number
(\(p < 0.01\), \(r = 0.14\)). BRCA2 significantly correlated with all
three of the genomic features tested: gene expression (\(p < 0.05\),
\(r = 0.10\)), copy number (\(p < 10^{-7}\), \(r = 0.23\)), and mutation
status (\(p < 0.001\)).

@@

\textbf{Should we do this?}

@@

Level-A G2P interpretations correspond to clinical evidence that
suggests efficacy of gene targets and/or drugs, and this work questions
whether these relationships manifest themselves in in vitro drug
screens. We have demonstrated that on its own, mutation status is not a
robust predictor of drug efficacy and that copy number and gene
expression fare better as predictors. However, for these three genomic
features in all three datasets, only 11.1\% (mutation status, 1 of 9,
CCLE) to 47.9\% (gene expression, 23 of 48, CTRP) (Table 2), of the
level-A G2P drug-gene associations in the respective dataset were
significant at an uncorrected \(\alpha = 0.05\). This suggests that
while the drug screens successfully identify some clinically relevant
drug-gene associations, many associations are also missed, which raises
the question of the extent to which clinical researchers can rely on in
vitro drug screens when attempting to develop and select therapeutics
for cancer patients.

@@

To preclude variation in genomic feature calls across the datasets, we
used identical annotations from CCLE for all cell lines screened in the
three datasets. The CCLE provided mutation annotations in 19,280 genes
across 1,596 cell lines (dataset: depmap\_18Q4\_mutation\_calls.csv,
accessed 14 November 2018). CCLE called substitutions using MuTect
(Cibulskis et al., 2013) and annotated variants using Oncotator (Ramos
et al., 2015) and indels using Indelocator
(\url{https://software.broadinstitute.org/cancer/cga/indelocator}). We
filtered mutation calls for point mutations, defined as
single-nucleotide insertions, deletions, and substitutions, regardless
of result, i.e.~frameshift or missense mutation. For this analysis, cell
lines harboring non-silent point mutations were considered
\enquote{mutant} for the gene in question. All other mutations and genes
without annotation in the Mutation Annotation Format (MAF) file were
considered \enquote{wildtype.} \enquote{Mutant} and \enquote{wildtype}
calls were binarily encoded per-gene/per-cell line, regardless of
quantity of harbored mutations per gene in a given cell line.

@@

The CCLE reports cell line sensitivity to small molecules as an activity
area measured above the dose-response curve (ActArea), while both CTRP
and GDSC report small molecule activity as area under the dose-response
curve (AUC). Since ActArea is reported with a scale of 0 to 8, we
converted CCLE's ActArea values to AUC via

@@

For \emph{Figure 1}, all data were imported and manipulated using pandas
(v0.23.0) (McKinney, 2011) and plotted using seaborn (v0.90) (Waskom,
2012), which sat on top of matplotlib (v2.2.2) (Hunter, 2007) and was
executed on Python (v2.7.15) (Python Software Foundation,
\url{https://www.python.org/}) in an IPython (v5.5.0) (Pérez \& Granger,
2007) kernel within a localhost Jupyter (v5.2.2) notebook (Kluyver et
al., 2016). All other analyses were conducted in R (v3.5.0) (R
Foundation for Statistical Computing, \url{https://www.R-project.org/})
in an RStudio environment (v1.1.447) (RStudio, 2012). All other plots
were drawn using the ggplot2 (v3.0.0) R package (Wickham, 2016).

@@

\hypertarget{ref-sirota2011}{}
Sirota, M., Dudley, J. T., Kim, J., Chiang, A. P., Morgan, A. A.,
Sweet-Cordero, A., \ldots{} Butte, A. J. (2011). Discovery and
preclinical validation of drug indications using compendia of public
gene expression data. \emph{Science Translational Medicine},
\emph{3}(96), 96ra77.
doi:\href{https://doi.org/10.1126/scitranslmed.3001318}{10.1126/scitranslmed.3001318}

@@

\hypertarget{ref-weinstein2013}{}
Weinstein, J. N., \& Lorenzi, P. L. (2013). Discrepancies in drug
sensitivity, \emph{504}(7480), 381--313.
doi:\href{https://doi.org/10.1038/504383a}{10.1038/504383a}
